---
title: 'Part 2:Basic Inferential Data Analysis Instructions'
author: "Nour Qweder"
date: "8/13/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)
library(ggplot2)
```
Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.
## 1.1.) Data analysis
Load the ToothGrowth data and perform some basic exploratory data analyses
Provide a basic summary of the data.


```{r, warning=FALSE}
set.seed(12345)
data("ToothGrowth")
attach(ToothGrowth)
head(ToothGrowth)
sapply(ToothGrowth, class)
summary(ToothGrowth)



n = dim(ToothGrowth)# 60 3
sapply(ToothGrowth,function(x) sum(is.na(x))) #see if there are NAN values per column
str(ToothGrowth)


plot(ToothGrowth)
```

From previous analysis, it can be noticed that *ToothGrowth* dataset with 60 observations and 3 features *len as a number value, supp as a factor and dose as a number value*.





## 1.2.) confidence intervals
Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)


```{r, echo=FALSE}
## applying t- test
test<-t.test(len~supp,data=ToothGrowth)

```

From the previous test, it can be noticed that *p_value = 0.6 > 0.5* ; Based on t-test, it can be obtained that supplement seems to have no impact on the growth of tooth 


```{r, echo=FALSE}
d1 <- ggplot(data = ToothGrowth, aes(y = supp, x = len, colour = len)) + geom_point()

d2 <- ggplot(data = ToothGrowth, aes(y = supp, x = len, colour = dose)) + geom_point()

d3 <- ggplot(data = ToothGrowth, aes(y = supp, x = len, colour = supp)) + geom_point()

grid.arrange(d1, d2,d3, nrow = 2, ncol = 2)
```

## Hypothesis
Length can be affected by dose

Application methods have no impact on tooth growth.
$H_{0}$ : Both group have the same mean.
$H_{A}$ : Means are different.

T-test

```{r}
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(1.0,0.5))
t.test(len~dose,data=ToothGrowth_sub)
```

## 1.3.) conclusions
From the previous test, it can be noticed that *p_value = 1.268e-07 < 0.05* ; Based on t-test, it can be obtained that does seems to have an impact on the growth of tooth, so $H_{0}$ can not be rejected.
