---
title: "Statistical Inference Course Project"
author: "Nour Qweder"
date: "8/13/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.2.) Simulations

```{r, warning=FALSE}
## Check for missing dependencies 
library(ggplot2)
library(lemon)
#install.packages("lemon")
knit_print.data.frame <- lemon_print
## init
lambda <- 0.2
n <- 40
sims <- 1:1000
set.seed(123)

# Simulate the draws
draws <- data.frame(x=sapply(sims, function(x) {mean(rexp(n, lambda))}))
#?rexp
# Plot 



p1 <- ggplot(draws, aes(x=x)) + 
  geom_histogram(
    col="red",
    aes(y=..count.., fill=..count..)) +
    scale_fill_gradient("Count", low="green", high="orange")+
    geom_density(colour="blue") +
  labs(title="Averages of 40 exponential over 1000 draws", y="Density", x="mean") 
p1

```
## 1.3.) Sample mean vs theoretical mean


```{r}
# Tabulating the Sample Mean & Theoretical Mean
sample.mean <- mean(draws$x)
theo.mean <- 1/lambda
mean.df1<-cbind(sample.mean, theo.mean)
knitr::kable(mean.df1)



```


```{r}
t.test(draws$x)[4]
```
From previous block, it can be noticed that sample mean and the theoretical mean approximately close.
Plus, after computing the confidence interval on the mean, it observed that the sample mean is between *[4.963824 5.059998]* at 95% confidence interval interval,



## 1.4.) Sample Variance vs theoretical Variance

```{r}
# Tabulating the Sample Mean & Theoretical Mean
sample.var <- var(draws$x)
theo.var <- (1/(lambda^2))/n
var.df<-cbind(sample.var, theo.var)
knitr::kable(var.df)



```

From previous block, it can be noticed that sample variance and the theoretical variance approximately close.
Plus, after computing the confidence interval on the variance, it observed that the sample variance is between *[0.6004928	0.625]* at 95% confidence interval interval,

## 1.5.) Distribution
```{r}

# Plotting Sample Mean & Varience vs Theoretical Mean & Varience
p2 <- ggplot(draws, aes(x=x)) +
  geom_histogram(aes(y=..density.., fill=..density..)) +
  scale_fill_gradient("Count", low="green", high="orange")+
  labs(title="Averages of 40 exponential over 1000 draws", y="Density", x="mean") + 
  geom_density(colour="blue") +
  geom_vline(xintercept=sample.mean, colour="red", linetype=2) +
  stat_function(fun=dnorm,args=list( mean=1/lambda, sd=sqrt(theo.var)),color = "blue") +
  geom_vline(xintercept=theo.mean, colour="blue", linetype=2) 
p2
```

